Air Quality and CMS Data

### 2021-10-07 code/data-analysis/config-file-generator.Rmd
plot, table, map
revision

---
title: "Config File Generator"
output: 
---

@@

@@

```{r ses adj. model for components - bz 6}
dataname <- "ndi-pmc-bz6.csv"
expo <- pmc.sub.yr

@@

```{r ses adj. model for components - bz 12}
dataname <- "ndi-pmc-bz12.csv"
expo <- pmc.sub.yr

@@

```{r ses adj. model for components - bz 24}
dataname <- "ndi-pmc-bz24.csv"
expo <- pmc.sub.yr

@@

>>>>

---
title: "Config File Generator"
author: "Fatemeh Kazemi"
date: "01-18-2021"
---

@@

```{r List of Major PM Components Yr Sub}
pmc.major.yr <- c("Yr1_SI","Yr1_NO3","Yr1_SO4",
                "Yr2_SI","Yr2_NO3","Yr2_SO4",
                "Yr3_SI","Yr3_NO3","Yr3_SO4",
                "Yr4_SI","Yr4_NO3","Yr4_SO4",
                "Yr5_SI","Yr5_NO3","Yr5_SO4")
```

@@

```{r ses adj. model for components - bz6}
dataname <- "ndi-pmc-bz6.csv"
expo <- pmc.sub.yr

@@

```{r ses adj. model for components - bz12}
dataname <- "ndi-pmc-bz12.csv"
expo <- pmc.sub.yr

@@

```{r ses adj. model for components - bz24}
dataname <- "ndi-pmc-bz24.csv"
expo <- pmc.sub.yr

@@

```{r ses adj. model for components - bz6 & 1-5yr}
dataname <- "ndi-pmc-bz6-15yr.csv"
expo <- pmc.major.yr

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz.sub),1)){
      w <- gsub("outcome", cuz.sub[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz.sub)*(i-1)
      writeLines(w, here('config-files','pmc-bz6-15yr', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - bz12 & 1-5yr}
dataname <- "ndi-pmc-bz12-15yr.csv"
expo <- pmc.sub.yr

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz.sub),1)){
      w <- gsub("outcome", cuz.sub[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz.sub)*(i-1)
      writeLines(w, here('config-files','pmc-bz12-15yr', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - bz 24 & 1-5yr}
dataname <- "ndi-pmc-bz24.csv"
expo <- pmc.sub.yr

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz.sub),1)){
      w <- gsub("outcome", cuz.sub[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz.sub)*(i-1)
      writeLines(w, here('config-files','pmc-bz24-15yr', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

### 2021-10-07 code/data-analysis/factor-analysis.Rmd
revision

### Last Edit: 12-31-2020

@@

@@

```{r Load datasets}
load(here('data','processed', 'pmc-daily.RDa'))
load(here('data','processed', 'aqs-sites.RDa'))
load(here('data','processed', 'mass-apportioned.RDa'))
```

```{r Call functions}
source(here('code','data-processors','air-data-smooth-mvavg-function.R'))
```

@@

factor.scores <- factor.scores(dt.pmc.daily %>% select(AS:OC), fit)
dt.fac.daily <- cbind(dt.pmc.daily %>% select(Site.ID, Date), factor.scores$scores) 
save(dt.fac.ec.daily, file = here('data', 'processed', 'fac-ec-daily.RDa'))
```

@@

```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
dt.air <- dt.fac.daily %>% 
  pivot_longer(cols = Factor1:Factor8,
               names_to = "Parameter.Symbol",
               values_to = "Value") %>% 
  arrange(Site.ID, Parameter.Symbol, Date)

@@

```{r Smoothing Data & Caluculating 1-yr mvavg for each month with EC}
dt.air <- dt.fac.daily.ec %>% 
  pivot_longer(cols = Factor1:Factor8,
               names_to = "Parameter.Symbol",
               values_to = "Value") %>% 
  arrange(Site.ID, Parameter.Symbol, Date)

@@

```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
dt.air <- dt.fac.residual %>% 
  pivot_longer(cols = PM_Factor1:PM_Factor8,
               names_to = "Parameter.Symbol",
               values_to = "Value") %>% 
  arrange(Site.ID, Parameter.Symbol, Date)

@@

@@

```{r - Single Tracer Mass Apportionment - function}
dt.sites <- dt.aqs.sites %>% 
  transmute(Site.ID,
            Latitude,
            Longitude,
            Location = ifelse(Location.Setting != "RURAL", "Urban", "Rural"),
            Region = ifelse(Region.IV == 1, "West",
                            ifelse(Region.IV == 2, "Midwest",
                                   ifelse(Region.IV == 3, "South", "Northeast"))))

Sources <- c("Soil", "Metals", "Traffic", "Biomass", "Coal", "Salt", "Oil", "Steel")

@@

```{r - Single Tracer Mass Apportionment - Combination 2}
dt.mass.app.c2 <- dt.pmc.daily %>% 
  mutate(Soil = so.coef(high.health, 'SI') * SI,
         Metals = so.coef(high.health, 'PB') * PB,
         Traffic = so.coef(high.health, 'NO3') * NO3,
         Biomass = so.coef(high.health, 'K') * K,
         Coal = so.coef(high.health, 'SO4') * SO4,
         Salt = so.coef(high.health, 'CL') * CL,
         Oil = so.coef(high.health, 'NI') * NI,
         Steel = so.coef(high.health, 'MN') * MN) %>% 
  select(Site.ID, Date, PM, Sources) %>% 
  inner_join(dt.sites) %>% 
  pivot_longer(cols = c('PM', Sources),
               names_to = "Source",
               values_to = "Mass")

>>>>

@@

# Notes
  1. Combination2 is better for mass app

@@

```{r Load datasets}
load(here('data','processed', 'pmc-daily.RDa'))
load(here('data','processed', 'aqs-sites.RDa'))
#load(here('data','processed', 'mass-apportioned-c1.RDa'))
```

```{r Call functions}
source(here('code','data-processors','air-data-smooth-mvavg-function.R'))

@@

factor.scores <- factor.scores(dt.pmc.daily %>% select(AS:OC), fit)
dt.fac.ec.daily <- cbind(dt.pmc.daily %>% select(Site.ID, Date), factor.scores$scores) 
save(dt.fac.ec.daily, file = here('data', 'processed', 'fac-ec-daily.RDa'))
```

@@

```{r Smoothing Factors & Caluculating 1-yr mvavg for each month}
dt.air <- dt.fac.daily %>% 
  pivot_longer(cols = Factor1:Factor8,
               names_to = "Parameter.Symbol",
               values_to = "Value") %>% 
  arrange(Site.ID, Parameter.Symbol, Date)

@@

```{r Smoothing Factors & Caluculating 1-yr mvavg for each month with EC}
dt.air <- dt.fac.ec.daily %>% 
  pivot_longer(cols = Factor1:Factor8,
               names_to = "Parameter.Symbol",
               values_to = "Value") %>% 
  arrange(Site.ID, Parameter.Symbol, Date)

@@

```{r Smoothing Factors Residuals & Caluculating 1-yr mvavg for each month}
dt.air <- dt.fac.residual %>% 
  pivot_longer(cols = PM_Factor1:PM_Factor8,
               names_to = "Parameter.Symbol",
               values_to = "Value") %>% 
  arrange(Site.ID, Parameter.Symbol, Date)

@@

```{r}
Factor.to.Index <- tribble(
  ~Index, ~Parameter,
   "Soil", "Factor1",
   "Metals", "Factor2",
   "Traffic", "Factor3",
   "Biomass", "Factor4",
   "Coal", "Factor5",
   "Salt", "Factor6",
   "Oil", "Factor7",
   "Steel", "Factor8"
   ) %>% 
  mutate(Index = as.factor(Index),
         Parameter = as.factor(Parameter))
```

```{r Factor Score Mass Apportionment}
dt.pm.daily <- dt.pmc.daily %>% 
  select(Site.ID, Date, PM)

dt.fac.pm.daily <- dt.fac.daily %>% 
  merge(dt.pm.daily) %>% 
  rename("Soil" = Factor1,
         "Metals" = Factor2,
         "Traffic" = Factor3,
         "Biomass" = Factor4,
         "Coal" = Factor5,
         "Salt" = Factor6,
         "Oil" = Factor7,
         "Steel" = Factor8)

factor.mass <- lmer(data = dt.fac.pm.daily,
              PM ~ Soil + Metals + Traffic + Biomass + Coal + Salt + Oil + Steel+ (1|Site.ID))

tab_model(factor.mass, show.se = T, show.ci = F, show.aic = T,
          show.re.var = F, show.icc = T, show.obs = T, show.ngroups = T,
          title = "Factor Related PM Mass")
```

```{r Smoothing Source mass & Caluculating 1-yr mvavg for each month}
dt.air <- dt.fac.pm.daily %>%
  mutate(Soil.mass = so.coef(factor.mass, 'Soil') * Soil,
         Metals.mass = so.coef(factor.mass, 'Metals') * Metals,
         Traffic.mass = so.coef(factor.mass, 'Traffic') * Traffic,
         Biomass.mass = so.coef(factor.mass, 'Biomass') * Biomass,
         Coal.mass = so.coef(factor.mass, 'Coal') * Coal,
         Salt.mass = so.coef(factor.mass, 'Salt') * Salt,
         Oil.mass = so.coef(factor.mass, 'Oil') * Oil,
         Steel.mass = so.coef(factor.mass, 'Steel') * Steel) %>% 
  select(Site.ID, Date, Soil.mass:Steel.mass) %>% 
  pivot_longer(cols = c(Soil.mass:Steel.mass),
               names_to = "Parameter.Symbol",
               values_to = "Value") %>% 
  arrange(Site.ID, Parameter.Symbol, Date)

dt.mass.app.1yr.fac <- para.monthly %>% 
  mutate(Parameter.Symbol = sub("\\..*", "", Parameter.Symbol),
         Year = floor(Date -0.01),
         Month = round((Date - Year)*12)) %>% 
  select(-Date) %>% 
  pivot_wider(names_sort = T,
              names_from = c(Parameter.Symbol),
              values_from = c(para.1yr)) %>% 
  arrange(Site.ID, Year, Month)

save(dt.mass.app.1yr.fac, file = here('data', 'processed', 'mass-app-1yr-fac.RDa'))
write.csv(dt.mass.app.1yr.fac, file = here('data', 'processed', 'mass-app-1yr-fac.csv'), row.names = F)
```

```{r IQR test}
Soil  <-  so.coef(factor.mass, 'Soil') * 0.38
Metals <- so.coef(factor.mass, 'Metals') * 0.16
Traffic <- so.coef(factor.mass, 'Traffic') * 1.18
Biomass <- so.coef(factor.mass, 'Biomass') * 0.18
Coal <- so.coef(factor.mass, 'Coal') * 1.03
Salt <- so.coef(factor.mass, 'Salt') * 0.18
Oil <- so.coef(factor.mass, 'Oil') * 0.09
Steel <- so.coef(factor.mass, 'Steel') * 0.15

# Second way
dt.mass.app.1yr.fac %>% summarise_at(vars(Biomass:Traffic), ~IQR(.x))
```

@@

```{r - Single Tracer Mass Apportionment}
dt.sites <- dt.aqs.sites %>% 
  transmute(Site.ID,
            Latitude,
            Longitude,
            Location = ifelse(Location.Setting != "RURAL", "Urban", "Rural"),
            Region = ifelse(Region.IV == 1, "West",
                            ifelse(Region.IV == 2, "Midwest",
                                   ifelse(Region.IV == 3, "South", "Northeast"))))

Sources <- c("Soil", "Metals", "Traffic", "Biomass", "Coal", "Salt", "Oil", "Steel")
```

@@

```{r - Single Tracer Mass Apportionment - Combination 2 - Preferred}
dt.mass.app.c2 <- dt.pmc.daily %>% 
  mutate(Soil = so.coef(high.health, 'SI') * SI,
         Metals = so.coef(high.health, 'PB') * PB,
         Traffic = so.coef(high.health, 'NO3') * NO3,
         Biomass = so.coef(high.health, 'K') * K,
         Coal = so.coef(high.health, 'SO4') * SO4,
         Salt = so.coef(high.health, 'CL') * CL,
         Oil = so.coef(high.health, 'NI') * NI,
         Steel = so.coef(high.health, 'MN') * MN) %>% 
  select(Site.ID, Date, PM, Sources) %>% 
  inner_join(dt.sites) %>% 
  pivot_longer(cols = c('PM', Sources),
               names_to = "Source",
               values_to = "Mass")

### 2021-10-07 code/data-analysis/output-cleaning.Rmd
plot, table, map
revision

---
title: "Analysis Output files"
---

@@

```{r Load data}
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))
load(here('data','processed','fac-ec-1yr.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
load(here('data','processed','pmc-sub-2yr-5yr.RDa'))
load(here('data','processed','pmc-sub-3yr-5yr.RDa'))
load(here('data','processed','pmc-sub-4yr-5yr.RDa'))
load(here('data','processed','pmc-sub-5yr.RDa'))
load(here('data','processed','mass-app-1yr-c2.RDa'))
```

```{r - Parameter/Factor to Index}
### Components
Para.to.Index <- tribble(
  ~Index, ~Parameter,
   "As", "AS",
   "Ca", "CA",
   "Cu", "CU",
   "Cl", "CL",
   "Fe", "FE",
   "Pb", "PB",
   "Mn", "MN",
   "Ni", "NI",
   "Mg", "MG",
   "Se", "SE",
   "V", "V",
   "Si", "SI",
   "Zn", "ZN",
   "K", "K",
   "Na", "NA",
   "NO3", "NO3",
   "SO4", "SO4",
   "OC", "OC",
   "EC", "EC",
   "PM2.5", "PM"
   ) %>% 
  mutate(Index = as.factor(Index),
         Parameter = as.factor(Parameter))

@@

```{r calculating IQRS}
### Components
pmc.1yr.iqr <- dt.pmc.site.ndi %>% 
  select(Site.ID) %>% 
  inner_join(dt.pmc.1yr) %>% 
  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
  pivot_longer(cols = AS:ZN,
               names_to = "Parameter",
               values_to = "IQR") %>% 
  mutate(Parameter = as.factor(Parameter))

### Factors excluding EC
fac.1yr.iqr <- dt.pmc.site.ndi %>% 
  select(Site.ID) %>% 
  inner_join(dt.fac.1yr) %>% 
  summarise_at(vars(Factor1:Factor8), ~IQR(.x)) %>% 
  pivot_longer(cols = Factor1:Factor8,
               names_to = "Parameter",
               values_to = "IQR")%>% 
  mutate(Parameter = as.factor(Parameter))

### Factors Inc EC
fac.ec.1yr.iqr <- dt.pmc.site.ndi %>% 
  select(Site.ID) %>% 
  inner_join(dt.fac.ec.1yr) %>% 
  summarise_at(vars(Factor1:Factor8), ~IQR(.x)) %>% 
  pivot_longer(cols = Factor1:Factor8,
               names_to = "Parameter",
               values_to = "IQR")%>% 
  mutate(Parameter = as.factor(Parameter))

### Source Apportioned PM Mass
mass.1yr.iqr <- dt.pmc.site.ndi %>% 
  select(Site.ID) %>% 
  inner_join(dt.mass.app.1yr.c2) %>% 
  summarise_at(vars(Biomass:Traffic), ~IQR(.x)) %>% 
  pivot_longer(cols = Biomass:Traffic,
               names_to = "Parameter",
               values_to = "IQR")%>% 
  mutate(Parameter = as.factor(Parameter))

@@

carbon.1yr.iqr <- dt.site %>% 
  select(Site.ID) %>% 
  inner_join(dt.carbon) %>% 
  summarise_at(vars(EC:OC), ~IQR(.x)) %>% 
  pivot_longer(cols = EC:OC,
               names_to = "Parameter",
               values_to = "IQR") %>% 
  mutate(Parameter = as.factor(Parameter))

@@

```

@@

out.pmc.sescat <- out.pmc.sescat %>% 
  mutate(Parameter = gsub(".*Yr_", "", Predictor),
         Parameter = as.factor(Parameter)) %>% 
  merge(pmc.1yr.iqr) %>% 
  merge(Para.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, SES.Cat, HR, HR.L, HR.U)

save(out.pmc.sescat, file = here('output','analysis','out-pmc-sescat.RDa'))
```

@@

>>>>

---
title: "Analysis Output files"
author: "Fatemeh Kazemi"
date: "01-30-2021"
---

@@

```{r Load data}
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))
load(here('data','processed','fac-ec-1yr.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
load(here('data','processed','pmc-sub-2yr-5yr.RDa'))
load(here('data','processed','pmc-sub-3yr-5yr.RDa'))
load(here('data','processed','pmc-sub-4yr-5yr.RDa'))
load(here('data','processed','pmc-sub-5yr.RDa'))
load(here('data','processed','mass-app-1yr-c2.RDa'))
load(here('data','processed','site-urban-ses-cat.RDa'))
```

```{r - Parameter/Factor to Index}
cmp <- c("PM2.5", "Si", "Ca", "Pb", "Zn", "NO3", "OC", "K", "Cu", "Se", "SO4",
         "Na", "Cl", "Ni", "V", "Fe", "Mn")

### Components
Para.to.Index <- tribble(
  ~Index, ~Parameter,
   "As", "AS",
   "Ca", "CA",
   "Cu", "CU",
   "Cl", "CL",
   "Fe", "FE",
   "Pb", "PB",
   "Mn", "MN",
   "Ni", "NI",
   "Mg", "MG",
   "Se", "SE",
   "V", "V",
   "Si", "SI",
   "Zn", "ZN",
   "K", "K",
   "Na", "NA",
   "NO3", "NO3",
   "SO4", "SO4",
   "OC", "OC",
   "EC", "EC",
   "PM2.5", "PM"
   ) %>% 
  mutate(Index = as.factor(Index),
         Parameter = as.factor(Parameter))

@@

```{r calculating IQRS}
### Components
pmc.1yr.iqr <- dt.pmc.1yr %>% 
  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
  pivot_longer(cols = AS:ZN,
               names_to = "Parameter",
               values_to = "IQR") %>% 
  mutate(Parameter = as.factor(Parameter))

### Factors excluding EC
fac.1yr.iqr <- dt.fac.1yr %>% 
  summarise_at(vars(Factor1:Factor8), ~IQR(.x)) %>% 
  pivot_longer(cols = Factor1:Factor8,
               names_to = "Parameter",
               values_to = "IQR")%>% 
  mutate(Parameter = as.factor(Parameter))

### Factors Inc EC
fac.ec.1yr.iqr <- dt.fac.ec.1yr %>% 
  summarise_at(vars(Factor1:Factor8), ~IQR(.x)) %>% 
  pivot_longer(cols = Factor1:Factor8,
               names_to = "Parameter",
               values_to = "IQR")%>% 
  mutate(Parameter = as.factor(Parameter))

### Source Apportioned PM Mass
mass.1yr.iqr <- dt.mass.app.1yr.c2 %>% 
  summarise_at(vars(Biomass:Traffic), ~IQR(.x)) %>% 
  pivot_longer(cols = Biomass:Traffic,
               names_to = "Parameter",
               values_to = "IQR")%>% 
  mutate(Parameter = as.factor(Parameter))

@@

carbon.1yr.iqr <- dt.carbon %>% 
  summarise_at(vars(EC:OC), ~IQR(.x)) %>% 
  pivot_longer(cols = EC:OC,
               names_to = "Parameter",
               values_to = "IQR") %>% 
  mutate(Parameter = as.factor(Parameter))

@@

table <- pmc.xyr.5yr.iqr %>% 
  mutate(IQR = ifelse(Parameter %in% c("PM", "NO3", "OC", "SO4"), IQR, IQR * 1000),
         IQR = sprintf("%0.2f", IQR)) %>% 
  pivot_wider(names_from = "Window",
              values_from = "IQR",
              names_sort = T) %>% 
  merge(Para.to.Index) %>% 
  rename(Component = Index) %>% 
  select(Component, everything(), -Parameter) %>% 
  filter(Component %in% cmp) %>% 
  mutate(Component = factor(Component, levels = cmp)) %>% 
  arrange(Component)

write.csv(table,
          file = here('output','table', '1to5iqr.csv'))

### Components - SES urban
pmc.1yr.sescat.iqr <- dt.site.urban.ses.cat %>% 
  inner_join(dt.pmc.1yr) %>% 
  group_by(ses.cat) %>% 
  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
  pivot_longer(cols = AS:ZN,
               names_to = "Parameter",
               values_to = "IQR") %>% 
  mutate(Parameter = as.factor(Parameter),
         SES.Cat = substr(ses.cat,1,1)) %>% 
  select(-ses.cat)
```

@@

out.pmc.sescat.upd <- out.pmc.sescat %>% 
  mutate(Parameter = gsub(".*Yr_", "", Predictor),
         Parameter = as.factor(Parameter)) %>% 
  merge(pmc.1yr.sescat.iqr) %>% #pmc.1yr.iqr
  merge(Para.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, SES.Cat, HR, HR.L, HR.U)

save(out.pmc.sescat.upd, file = here('output','analysis','out-pmc-sescat-upd.RDa'))
```

@@

```{r Output PMC Bufferzone and Exposure window}
out.pmc.buffer.expo = data.frame()
for (i in c("6", "12", "24")){
  dt <- read.csv(here('output','analysis',paste('pmc-bz',i,'-15yr.csv', sep= ""))) %>% 
    mutate(Buffer = i,
           Window = substr(Predictor, 3,3))
  out.pmc.buffer.expo  <-  rbind(out.pmc.buffer.expo, dt)
}

out.pmc.buffer.expo <- out.pmc.buffer.expo %>% 
  mutate(Parameter = gsub(".*_", "", Predictor),
         Parameter = as.factor(Parameter)) %>% 
  merge(pmc.xyr.5yr.iqr) %>% 
  merge(Para.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config, Buffer) %>% 
  select(Index, Cause, Buffer, Window, HR, HR.L, HR.U)

save(out.pmc.buffer.expo, file = here('output','analysis','out-pmc-buffer-expo.RDa'))
```

### 2021-10-07 code/data-processors/cms-data-processor.Rmd
revision

```{r load data}
dirUSSpatial <- 'C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\'
load(paste0(dirUSSpatial,'ses-site-bz12.RDa'))
load(paste0(dirUSSpatial,'ses-site-bz6.RDa'))
load(paste0(dirUSSpatial,'ses-site-bz24.RDa'))
load(paste0(dirUSSpatial,'brfss-site.RDa'))
load(here('data','processed','master-ndi-pmc.RDa'))
load(here('data','processed','master-ndi-pmc-race.RDa'))
load(here('data','processed','master-ndi-pmc-bz6.RDa'))
load(here('data','processed','master-ndi-pmc-bz12.RDa'))
load(here('data','processed','master-ndi-pmc-bz24.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))
load(here('data','processed','fac-ec-1yr.RDa'))
load(here('data','processed','pmc-residual-1yr.RDa'))
load(here('data','processed','fac-residual-1yr.RDa'))
load(here('data','processed','pmc-sub-5yr.RDa'))
load(here('data','processed','pmc-sub-4yr-5yr.RDa'))
load(here('data','processed','pmc-sub-3yr-5yr.RDa'))
load(here('data','processed','pmc-sub-2yr-5yr.RDa'))
load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
load(here('data','processed','mass-app-1yr-c2.RDa'))
```

@@

@@

@@

>>>>

```{r load data}
dirUSSpatial <- 'C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\'
load(paste0(dirUSSpatial,'ses-site-bz12.RDa'))
load(paste0(dirUSSpatial,'ses-site-bz6.RDa'))
load(paste0(dirUSSpatial,'ses-site-bz24.RDa'))
load(paste0(dirUSSpatial,'brfss-site.RDa'))
load(here('data','processed','master-ndi-pmc.RDa'))
load(here('data','processed','master-ndi-pmc-race.RDa'))
load(here('data','processed','master-ndi-pmc-bz6.RDa'))
load(here('data','processed','master-ndi-pmc-bz12.RDa'))
load(here('data','processed','master-ndi-pmc-bz24.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))
load(here('data','processed','fac-ec-1yr.RDa'))
load(here('data','processed','pmc-residual-1yr.RDa'))
load(here('data','processed','fac-residual-1yr.RDa'))
load(here('data','processed','pmc-sub-5yr.RDa'))
load(here('data','processed','pmc-sub-4yr-5yr.RDa'))
load(here('data','processed','pmc-sub-3yr-5yr.RDa'))
load(here('data','processed','pmc-sub-2yr-5yr.RDa'))
load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
load(here('data','processed','mass-app-1yr-c2.RDa'))
load(here('data','processed','mass-app-1yr-fac.RDa'))
```

@@

save(dt.site.urban.ses.cat, file = here('data', 'processed', 'site-urban-ses-cat.RDa'))

dt.site.urban.ses.cat %>% 
  distinct(Site.ID) %>% 
  group_by(ses.cat) %>% 
  summarise(n = n())

dt.site.urban.ses.cat %>% 
  group_by(ses.cat) %>% 
  summarise(n = n())

@@

```{r PM Apportioned Mass with Factors}
dt.mass <- dt.mass.app.1yr.fac %>% 
  rename_at(vars(Biomass: Traffic), ~paste("Yr", .x, sep = "_"))

dt.ndi.mass.fac <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
  inner_join(dt.mass) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.mass.fac, 
          file = here('data', 'processed', 'ndi-mass-fac.csv'),
          row.names = F)
```

@@

```{r}
cmp.major <- c("SI", "NO3", "SO4")

dt.pmc5 <- dt.pmc.5yr %>% 
  select(Site.ID, Year, Month, cmp.major) %>% 
  rename_at(cmp.major, ~paste("Yr5", .x, sep = "_"))

dt.pmc4 <- dt.pmc.4yr.5yr %>% 
  select(Site.ID, Year, Month, cmp.major) %>% 
  rename_at(cmp.major, ~paste("Yr4", .x, sep = "_"))

dt.pmc3 <- dt.pmc.3yr.5yr %>% 
  select(Site.ID, Year, Month, cmp.major) %>% 
  rename_at(cmp.major, ~paste("Yr3", .x, sep = "_"))

dt.pmc2 <- dt.pmc.2yr.5yr %>% 
  select(Site.ID, Year, Month, cmp.major) %>% 
  rename_at(cmp.major, ~paste("Yr2", .x, sep = "_"))

dt.pmc1 <- dt.pmc.1yr.5yr %>% 
  select(Site.ID, Year, Month, cmp.major) %>% 
  rename_at(cmp.major, ~paste("Yr1", .x, sep = "_"))

dt.pmc.major <- dt.pmc1 %>% 
  merge(dt.pmc2) %>% merge(dt.pmc3) %>% 
  merge(dt.pmc4) %>% merge(dt.pmc5)

```{r PMC BZ6 - 1-5yr}
dt.ses <- dt.ses.site.bz6 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.pmc.bz6.15yr <- dt.master.ndi.pmc.bz6 %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
  inner_join(dt.pmc.major) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.pmc.bz6.15yr, 
          file = here('data', 'processed', 'ndi-pmc-bz6-15yr.csv'),
          row.names = F)
```

```{r PMC BZ 12 - 1-5yr}
dt.ses <- dt.ses.site.bz12 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.pmc.bz12.15yr <- dt.master.ndi.pmc.bz12 %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
  inner_join(dt.pmc.major) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.pmc.bz12.15yr, 
          file = here('data', 'processed', 'ndi-pmc-bz12-15yr.csv'),
          row.names = F)
```

```{r PMC BZ 24 - 1-5yr}
dt.ses <- dt.ses.site.bz24 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.pmc.bz24.15yr <- dt.master.ndi.pmc.bz24 %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
  inner_join(dt.pmc.major) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.pmc.bz24.15yr, 
          file = here('data', 'processed', 'ndi-pmc-bz24-15yr.csv'),
          row.names = F)
```
